Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC

### 2024-11-26 paper/manuscript.Rmd
add README files for project and data explanation, add comments to analysis script, update figures for production

@@

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany"
  - id            : "3"
    institution   : "School of Psychology, University of Auckland, New Zealand"
  - id            : "4"
    institution   : "Université Marien Ngouabi, Republic of the Congo"
  - id            : "5"
    institution   : "Department of Psychology, Stanford University, USA"
  - id            : "6"
    institution   : "School of Psychology, University of Plymouth, UK"
  - id            : "7"
    institution   : "Department of Psychology, Koç University, Türkiye"
  - id            : "8"
    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
  - id            : "9"
    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
  - id            : "10"
    institution   : "Department of Psychology, Georgia State University, USA"
  - id            : "11"
    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
  - id            : "12"
    institution   : "Department of Psychology, University of York, UK"
  - id            : "13"
    institution   : "Budongo Conservation Field Station, Uganda"
  - id            : "14"
    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
  - id            : "+"
    institution   : "joint last author"

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    keep_tex: true
editor_options    : 
  markdown: 
    wrap: sentence
bibliography      : "../../references.bib"
---

>>>>

    affiliation   : "14,15"

@@

affiliation:
  - id            : "1"
    institution   : "Institute of Psychology in Education, Leuphana University Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany"
  - id            : "3"
    institution   : "School of Psychology, University of Auckland, New Zealand"
  - id            : "4"
    institution   : "Université Marien Ngouabi, Republic of the Congo"
  - id            : "5"
    institution   : "Department of Psychology, Stanford University, USA"
  - id            : "6"
    institution   : "School of Psychology, University of Plymouth, UK"
  - id            : "7"
    institution   : "Department of Psychology, Koç University, Türkiye"
  - id            : "8"
    institution   : "Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK"
  - id            : "9"
    institution   : "Department of Psychology and Social Work, University of Namibia, Namibia"
  - id            : "10"
    institution   : "Department of Psychology, Georgia State University, USA"
  - id            : "11"
    institution   : "Department of Psychology, Developmental Psychology, Uppsala University, Sweden"
  - id            : "12"
    institution   : "Department of Psychology, University of York, UK"
  - id            : "13"
    institution   : "Budongo Conservation Field Station, Uganda"
  - id            : "14"
    institution   : "CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China"
  - id            : "15"
    institution   : "Department of Cognitive Sciences, University of California Irvine, USA"
  - id            : "+"
    institution   : "joint last author"

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_word
editor_options    : 
  markdown: 
    wrap: sentence
bibliography      : "../../references.bib"
---

### 2024-11-26 paper/manuscript.tex
add README files for project and data explanation, add comments to analysis script, update figures for production

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC},
  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)3, Ardain Dzabatou4, Michael C. Frank (ORCID: 0000-0002-7551-4378)5, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)3, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)6, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)7, Bahar Köymen (ORCID: 0000-0001-5126-8240)8, Maira V. Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)9, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R. Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2,10, Umay Sen (ORCID: 0000-0001-9488-0851)11, Katie Slocombe (ORCID: 0000-0002-7310-1887)12, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime13, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)14, Yufei Zong (ORCID: 0009-0000-5012-0244)14, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC}
\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Ardain Dzabatou\textsuperscript{4}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{5}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{6}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{7}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{8}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{9}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2,10}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{11}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{12}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{13}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{14}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{14}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Georgia State University, USA\\\textsuperscript{11} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{12} Department of Psychology, University of York, UK\\\textsuperscript{13} Budongo Conservation Field Station, Uganda\\\textsuperscript{14} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}

@@

\bibitem[\citeproctext]{ref-prein2024variation}
Prein, J. C., Maurits, L., Werwach, A., Haun, D. B. M., \& Bohn, M. (2024). Variation in gaze following across the life span: {A} process-level perspective. \emph{Developmental Science}, Article e13546. \url{https://doi.org/10.1111/desc.13546}

>>>>

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC},
  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)3, Ardain Dzabatou4, Michael C. Frank (ORCID: 0000-0002-7551-4378)5, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)3, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)6, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)7, Bahar Köymen (ORCID: 0000-0001-5126-8240)8, Maira V. Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)9, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R. Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2,10, Umay Sen (ORCID: 0000-0001-9488-0851)11, Katie Slocombe (ORCID: 0000-0002-7310-1887)12, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime13, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)14, Yufei Zong (ORCID: 0009-0000-5012-0244)14,15, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC}
\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Ardain Dzabatou\textsuperscript{4}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{5}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{6}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{7}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{8}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{9}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2,10}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{11}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{12}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{13}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{14}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{14,15}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Georgia State University, USA\\\textsuperscript{11} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{12} Department of Psychology, University of York, UK\\\textsuperscript{13} Budongo Conservation Field Station, Uganda\\\textsuperscript{14} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{15} Department of Cognitive Sciences, University of California Irvine, USA\\\textsuperscript{+} joint last author}

@@

\bibitem[\citeproctext]{ref-prein2024variation}
Prein, J. C., Maurits, L., Werwach, A., Haun, D. B. M., \& Bohn, M. (2024). Variation in gaze following across the life span: {A} process-level perspective. \emph{Developmental Science}, \emph{27}(6), e13546. \url{https://doi.org/10.1111/desc.13546}
